### 2018-01-30 includes/experiment.tex
add section labels; remove manual spacing; fix sectioning
explain analysis a bit more carefully

\section{Experimental Data}
\label{sec:data}
\vspace{-0.1in}

@@

\section{Usefulness to \us{}: A Case Study}
\vspace{-0.1in}

        We describe the defects and missing heuristics exposed by \fuzzer{} to illustrate why \fuzzer{} is a valuable asset in solver development.

\vspace{-0.15in}
\subsection{Defects discovered and fixed in \us{}}
\vspace{-0.1in}

@@

\vspace{-0.15in}    
\subsection{Solving heuristics}
\vspace{-0.1in}

>>>>

\section{Experimental Data}
\label{sec:data}

@@

\section{Usefulness to \us{}: A Case Study}
\label{sec:analysis}

        In this section we describe a number of performance-related issues and opportunities for new heuristics
        which were exposed in \us{} by \fuzzer{} to illustrate the utility and value of the tool in solver development.

\subsection{Defects discovered and fixed in \us{}}

@@

\subsection{Solving heuristics}

### 2018-01-30 includes/introduction.tex
explain analysis a bit more carefully

        \begin{enumerate}
            \item \textbf{The \fuzzer{} tool}: We describe in Section~\ref{sec:fuzzer} a modular fuzzer which can transform and generate \smtfull{} string and regex problems. We briefly document its components and modular architecture. We provide example use cases to demonstrate its usefulness as an exploratory tool for validating solvers. We additionally detail its regex generation and transformation capabilities.
            \item \textbf{A repository of \smtfull{} problems}: We present a repository of \smtfull{} string and regex problem suites we generated using \fuzzer{} in Section~\ref{sec:problems}. We demonstrate the usefulness of these suites by revealing specific defects they helped uncover and fix in \us{}.
            \item \textbf{Experimental Results}: We compare \theSolvers{} on the \fuzzer{} suites and selectively present the experimental result on \theSuites{} in Section~\ref{sec:data}. We highlighted these suites because they uniquely made some solvers perform poorly, but not others.
            \item \textbf{Analysis}: We analyze our experimental results in Section~\ref{sec:analysis} by inspecting the execution traces of the solvers on the given problems. For \us{}, we pinpoint algorithmic limitations that cause poor performance. For other solvers, we draw superficial conclusions based solely on the execution traces, and invite their authors to conduct further analysis.
        \end{enumerate}

>>>>

        \begin{enumerate}
            \item \textbf{The \fuzzer{} tool}: We describe in Section~\ref{sec:fuzzer} a modular fuzzer which can transform and generate \smtfull{} string and regex problems. We briefly document its components and modular architecture. We provide example use cases to demonstrate its usefulness as an exploratory tool for validating solvers. We additionally detail its regex generation and transformation capabilities.
            \item \textbf{A repository of \smtfull{} problems}: We present a repository of \smtfull{} string and regex problem suites we generated using \fuzzer{} in Section~\ref{sec:problems}. We demonstrate the usefulness of these suites by revealing specific defects they helped uncover and fix in \us{}.
            \item \textbf{Experimental Results}: We compare \theSolvers{} on the \fuzzer{} suites and selectively present the experimental result on \theSuites{} in Section~\ref{sec:data}. We highlighted these suites because they uniquely made some solvers perform poorly, but not others.
            \item \textbf{Analysis}: We analyze our experimental results in Section~\ref{sec:analysis} by inspecting the execution traces of the solvers on the given problems. We pinpoint algorithmic limitations in \us{} that cause poor performance, and analyze proposed and implemented enhancements that address the issues which \fuzzer{} helped us to identify.
        \end{enumerate}
